---
title: "Developing Data Products Week 2"
author : "Suhas P K"
date: "`r Sys.Date()`"
output:
  rmdformats::downcute:
    self_contained: true
    default_style: "dark"
    downcute_theme: "default"
---


```{r setup, include=FALSE}
## Global options
knitr::opts_chunk$set(cache = TRUE)
```

## Objective

Create a web page using R Markdown that features a map created with Leaflet. 

Host your webpage on either GitHub Pages, RPubs, or NeoCities.

Your webpage must contain the date that you created the document, and it must contain a map created with Leaflet.

## Review Criteria

The rubric contains the following two questions:

- Does the web page feature a date and is this date less than two months before the date that you’re grading this assignment?

- Does the web page feature an interactive map that appears to have been created with Leaflet?

## Assignment

```{r libraries}
if (!require(leaflet)){
  install.packages("leaflet")
  library(leaflet)
}

```

Here, I want a map of bangalore with some famous eateries. For that I need a data frame having the coordinates of these places and the name of the eateries.

```{r my data frame, comment = ""}
lat <- c(12.94731, 12.94861, 12.93770, 12.95536, 12.94486)
long <- c(77.57148,77.59892, 77.57995,  77.58554, 77.56046)
eat_name <- c("MLTR","Janatha Hotel", "Hotel Sanman", "MTR", "Hotel Mangala")

df <- data.frame(eat_name,lat,long)
head(df)
```
Using leaflet and mapping the coordinates.

```{r hotel map}
m <- leaflet() %>% 
  addTiles() %>% 
  addMarkers(lat = df$lat, 
             lng = df$long,
             label = df$eat_name,
             labelOptions = labelOptions(noHide = T, textsize = "15px"))

m
```

## Mapping Clusters

When you zoom in to each cluster, the cluster will separate until individual markers are visible.

```{r cluster points, comment= ""}
cluster_points <- data.frame(
  lat = runif(500, min = 12.92, max = 12.96),
  lng = runif(500, min = 77.5, max = 77.6)
) 

```

```{r}
cluster_points %>% 
  leaflet() %>% 
  addTiles() %>% 
  addMarkers(clusterOptions = markerClusterOptions())
```






















